IALE 2015 Analysis

### 2015-07-03 iale2015_sem.Rmd
added canopy cover estimates for the plots from the spherical densiometer calculations

```{r load data}
# Ecological data: leaf counts, infection
load("~/GitHub/superspreaders/stems_plots.RData")
# Vegetation data
veg_us_2005 <- read.csv("analysis/data/understory_veg_2005.csv")
veg_us_2011 <- read.csv("analysis/data/understory_veg_2011.csv")
# Untagged dbh data
untagged_dbh <- read.csv("analysis/data/untagged_dbh_summary.csv")

@@

Now I want to join the richness data set to the `plots_umca` data frame that currently has the environmental and leaf count/infection variables.

@@

plots_umca <- left_join(plots_umca, richness, by = c("plotid", "year"))
```

@@

Now that I have summarized some vegetation (not species specific), environmental, and bay laurel disease data to the plot-level I want to join this to the plot-level oak infection data.

@@

filter(oak_sod, year == 2003) # 87 records
filter(oak_sod, year == 2004) # 90 records
# 2005 appears to be the first full year of observing all the plots
filter(oak_sod, year == 2005) # 171 records
filter(oak_sod, year == 2006) # 172 records
filter(oak_sod, year == 2007) # 171 records
filter(oak_sod, year == 2008) # 171 records
filter(oak_sod, year == 2009) # 170 records
filter(oak_sod, year == 2010) # 170 records
filter(oak_sod, year == 2011) # 170 records; final year of Sarah's 2nd chapter
filter(oak_sod, year == 2012) # 169 records
filter(oak_sod, year == 2014) # 168 records
# In Sarah's analysis we end up using only 163 plots
```

>>>>

```{r load data}
# Ecological data: leaf counts, infection
load("~/GitHub/superspreaders/stems_plots.RData")
# Vegetation data
veg_us_2005 <- read.csv("analysis/data/understory_veg_2005.csv")
veg_us_2011 <- read.csv("analysis/data/understory_veg_2011.csv")
# Untagged dbh data
untagged_dbh <- read.csv("analysis/data/untagged_dbh_summary.csv")
canopy_cover <- read.csv("analysis/data/plot_canopy_cover_dens.csv")

@@

Now I want to join the richness data set and the canopy cover estimates to the `plots_umca` data frame that currently has the environmental and leaf count/infection variables.

@@

plots_umca <- left_join(plots_umca, richness, by = c("plotid", "year"))
head(canopy_cover)
canopy_cover <- select(canopy_cover, plotid, year, pct_cvr)
plots_umca <- left_join(plots_umca, canopy_cover, by = c("plotid", "year"))
```

@@

Now that I have summarized some vegetation (not species specific), environmental, and bay laurel disease data to the plot-level I want to join this and the canopy cover data to the plot-level oak infection data.

@@

oak_sod <- left_join(oak_sod, canopy_cover, by = c("plotid", "year"))

filter(oak_sod, year == 2003) # 86 records
filter(oak_sod, year == 2004) # 88 records
# 2005 appears to be the first full year of observing all the plots
filter(oak_sod, year == 2005) # 170 records
filter(oak_sod, year == 2006) # 172 records
filter(oak_sod, year == 2007) # 171 records
filter(oak_sod, year == 2008) # 171 records
filter(oak_sod, year == 2009) # 170 records
filter(oak_sod, year == 2010) # 170 records
filter(oak_sod, year == 2011) # 170 records; final year of Sarah's 2nd chapter
filter(oak_sod, year == 2012) # 169 records
filter(oak_sod, year == 2014) # 168 records
# In Sarah's analysis we end up using only 163 plots
```
